Predicting children's and adults' preferences in physical interactions via physics simulation

### 2021-02-04 paper/paper2021.Rmd
extra para
final edits

## Method
<!-- \vspace{-4pt} -->
### Participants
200 adults were recruited via Amazon Mechanical Turk and were paid $1 for participating.

### Materials
<!-- \vspace{-4pt} -->
Stimuli were images of 3D objects produced using Blender 3D-modeling software. 
The nine objects, depicted in Figure 1, were bowl, cone, dumbbell, octahedron, pentagon (pentagonal prism), pipe, pyramid, torus, triangular prism, and ball (sphere; not pictured).

@@

### Design
<!-- \vspace{-4pt} -->
The experiment consisted of 20 drop trials, completed by each participant in one of four pseudorandom orders.
Participants were randomly assigned to each order.
Each drop trial displayed an object X that is to be dropped on one of two other objects (Y or Z), as described in the following procedure.
In the 20 trials, each of the above 3D objects was used twice as the drop object (X), and appeared four times as potential targets.
Instead of randomly sampling the target objects (Y or Z), each trial was designed to allow for one of two goal relations (or affordances): containment, or support.
That is, the target objects were chosen so that one of them would be capable of either supporting or  containing the dropped object.
For example, if asked to drop the cone on either the torus or the octahedron, a containment relation could be achieved between the cone and the torus, but not the octahedron (and support is unlikely due to the small surface area of the octahedron).
An example support relation is choosing to drop the pentagonal prism on the (equal diameter) pipe rather than the pyramid.
10 of the 20 trials were designed to afford containment relations, and the other 10 afforded support relations.
We refer to the objects affording the designed containment and support relations as *targets*, and the alternative objects as *distractors*.
Distractors for each trial were the same for all participants, and were selected to 1) not afford containment/support of the dropped object, and 2) roughly equate the frequency of appearance of all 10 objects.

@@

```{r fig2-task, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=3.4, fig.height=3.3, set.cap.width=T, num.cols.cap=1, fig.cap = "Example of a trial given to adults in Experiment 1."}
img <- png::readPNG("figs/2AFC_DropTaskFig.png")
grid::grid.raster(img)
```

@@

## Results
We analyzed data from the `r Nad` adults who completed the experiment and answered at least 3 of the 4 catch trials correctly (45 participants were excluded for not meeting this criterion).
<!-- The main questions of interest are 1) are adults consistent in their preference of drop-target combinations? 2) are they more consistent with trials that afford support or containment relations? and 3) are there other apparent factors that drive their preferences? Our analysis addresses each question in turn. -->
Averaging each subject's binary responses (1=target relation, 0=alternative) for each trial type revealed a stronger preference for containment relations ($M=$ `r round(ad_rel_means[1,]$M,2)`) than support relations ($M=$ `r round(ad_rel_means[2,]$M,2)`; paired `r t_apa(ad_supp_cont, format="rmarkdown", print=F)`).
Table 1 shows the proportion of participants that chose the designed target relation for each of the 20 trials. <!-- [should also show alternative target object?]. -->
Based on the binomial distribution, any of the trials on which more than 90 of the 155 participants agree (i.e., >0.59 or <0.41) significantly differ from chance. 
As can be seen in Table 1, adults participants (*adult* column) significantly preferred the target relation for all 10 of the containment trials, and significantly preferred five targets on the 10 support trials; the other five support trials did not significantly differ from chance, suggesting that many participants found the prospect of dropping on the distractor object at least equally enticing.

@@

# Experiment 2: Children
<!-- \vspace{-4pt} -->
Experiment 1 demonstrated that adults show consistent preferences for dropping objects on target objects that afford containment relations, and to a lesser extent support relations. 
Experiment 2 investigates whether these strong preferences are present even in young children, recognizing that children may find different types of physical interactions (e.g., rolling, bouncing, unpredictability) of greater interest than adults, or may simply show more idiosyncratic choice patterns.

## Method
<!-- \vspace{-4pt} -->
We adapted the same materials and procedure used in Experiment 1 for use in an online experiment with children, in order to directly compare the results for children and adults.

### Participants
<!-- \vspace{-4pt} -->
Participants were 73 children recruited online via outreach through a local nursery school and targeted Facebook ads over the course of 6 months.
Participant exclusions were made based on cases where i) the participant did not complete more than half of the study play session or ii) the parent did not consent for video recording of study. 
After exclusions, results from `r Nch` were analyzed, including `r age[1,]$N` 3-year-olds, `r age[2,]$N` 4-year-olds, `r age[3,]$N` 5-year-olds, `r age[4,]$N` 6-year-olds, and `r age[5,]$N` 7-year-olds.

### Materials
<!-- \vspace{-4pt} -->
The materials were the same as those used in Experiment 1, except that the trials were adapted for presentation via Zoom in a slide presentation as shown in Figure 3. 
<!-- Introductory slides were added for informed consenting process and screen configuration, where the researcher's video was placed directly below drop object X and in between target objects Y and Z (see Figure 3). -->

@@

### Procedure
<!-- \vspace{-4pt} -->
<!-- Based on piloting, we estimated the activity would require 10 minutes to complete. -->
After the parent provided informed consent, children were assigned to one of two pseudorandom trial orders in counterbalanced order.
<!-- A video recording was taken of the online session. -->
To accompany the practice trial, children were shown 3D-printed instances of the three physical objects held by the researcher, to ensure that children understood their physicality. 
Children were asked to verbally select target object Y or Z, and then asked to confirm whether they wanted to select the object on the red or green side of the screen, in order to prevent left/right confusion. 
The sides on which target objects and colors appeared were counterbalanced across trials.

## Results
<!-- \vspace{-4pt} -->
<!-- Were children more consistent in their choices on support or containment trials? -->
Similar to adults, averaging each child's binary responses for each trial type revealed a stronger preference for containment relations ($M=$ `r round(ch_rel_means[1,]$M,2)`) than support relations ($M=$ `r round(ch_rel_means[2,]$M,2)`; paired `r t_apa(ch_supp_cont, format="rmarkdown", print=F)`). 
Unlike adults, however, children did not show a significant preference for choosing the support relation. <!-- [add a regression with trial_type * age (3 - 18=adult)?] -->
Figure 4 shows the proportion of participants' choice of the designed target relation broken down by relation type and age group. Preferences increased with age and were overall stronger for containment.

<!-- We next examined children's choice of target objects to determine if children were choosing randomly, or had consistent preferences for some objects.  -->
We next examined trial-level effects in children. Table 1 shows the proportion of children ("child" column) choosing the designed target relation for each of the 20 trials, alongside the adult choice proportions from Experiment 1. 
Based on the binomial distribution, any of the trials on which more than 41 of the 66 participants agree (i.e., >0.64 or <0.36) significantly differ (*p*<.05) from chance. <!-- stricter crit for mult comparisons? Bonf=.0025 -->
Children significantly preferred the designed relation on eight of the 10 containment trials, while only significantly preferring two of the 10 support relation choices.
On the remaining two containment trials and the other eight support trials, children's preferences also did not significantly differ from chance against the designed relation.
These item effects were relatively reliable, though noisier than that of adults: the split-half reliability for children's choices was *r* = `r round(mean(sh_subj_child), 2)` (sd=`r round(sd(sh_subj_child), 2)`).
The split-half reliability of children's choices on containment trials was *r* = `r round(mean(sh_ch_contain), 2)` (sd=`r round(sd(sh_ch_contain), 2)`), and on support trials was *r* = `r round(mean(sh_ch_support), 2)` (sd=`r round(sd(sh_ch_support), 2)`).

@@

### Comparison of Children's vs. Adults' Preferences
<!-- \vspace{-4pt} -->
<!-- Finally, we compared the trial-level preferences of children and adults. -->
Figure 5 shows adults' (Experiment 1) vs. children's (Experiment 2) choice proportions for the target relations, colored by relation type (visualizing the same data presented in Table 2, but with 95% CIs).
If adults' and children's judgments corresponded perfectly, they would fall along the dotted $y=x$ line, but children's preferences mostly fall short of that line, lying closer to the chance line ($y=0.5$).
At a glance, these results seem to support the hypothesis that "children are noisy adults" in this task as well as suggesting some consistency in the trial-level effects across development. 
This consistency also confers additional motivation for attempting to understand what drives human interest in particular physical interactions in this task through computational models.

@@

# Comparison to Physics Simulations
<!-- \vspace{-4pt} -->
```{r load-model-data}
load(here("models/model_data.RData")) # mdat, all_trials_mse, all_trials_mse_r, etc.
load(here("models/support_probability_fit_df.RData")) 
# ad_df, ch_df - model (w SD) vs. human (need 95%CIs)

@@

For each trial's two possible drop object choices, we ran 250 simulated drops, and for each drop we calculated a variety of features measuring the state of the model after the drop was completed.
We selected features that we thought may provide good metrics for what people could find interesting, for instance, the mean amount of time before both objects come to rest (*M(Move Time)*), as well as the standard deviation of that time (*SD(Move Time)*).
Some features were calculated separately for drop and target objects, such as how variable each object's final positions tend to be (e.g., the inverse SD of each object's final position (*1/SD(Drop Obj Pos)* and *1/SD(Target Pos)*), the mean and maximum final distance of each object from the drop location (e.g., *M(Target Dist)* and *Max(Target Dist)*), and how variable the speed of each objects tend to be after collision (e.g., *Vel(Target)*).
<!-- SD of the normed velocity of each object after first collision (e.g.,  -->
We also tested a variety of features based on the likelihood of the dropped object coming to rest atop the target object--$Pr(support)$--and the robustness of this likelihood to small perturbations in drop position (*Supp. Sharpness*).
Note that the model's definition of support does not explicitly distinguish support from containment.

@@

Overall, a few of these features were modestly correlated with people's choices. Table 2 shows the correlation between model preferences (with softmax $\beta = 1$) vs. adults' and children's choice proportions, both to all trials and separately for containment and support trials.
When all trials were considered together, the feature with the strongest correlation to adults' choices was the velocity of the target object (*Vel(Target)*, $r=.33$), while the feature with the strongest correlation to children's choices was *Support Sharpness* (see Methods, $r=.18$)
<!-- For support trials, both adults' ($r=.39$) and children's ($r=.41$) choices were best correlated with a feature indexing the variability in the target object's final position (*1/SD(Target Pos)*).  -->
<!-- For containment trials, adults' choices were most correlated with the velocity of the dropped object (*Vel(Drop Obj)*, $r=.54$) which also showed a modest correlation with children's choices ($r=.41$); however, children's choices were most correlated with the maximum distance of the target object (*Max(Target Dist)*, $r=.43$).  -->
Many of the other features showed weak or even moderate negative correlations with people's choices.

Examination of the models with $\beta$ optimized, in contrast, revealed that none  achieved a good fit to human preferences. While the best-fitting feature, *Pr(support)*, captured both adults' and children's overall mean preference for the designed target relations, it explained essentially no trial-level variation and was in fact negatively correlated with choices. This was not due to noisy behavioral data: while the noise ceiling on choice preferences for all trials was $r$=.97 for adults and $r$=.76 for children, the best fitting feature only achieved XX.

@@

# combine all_trials, supp_trials, and cont_trials
mod_tab <- all_trials %>% select(-mse) %>%
  rename(`All` = r) %>% 
  left_join(supp_trials) %>%
  left_join(cont_trials) %>%
  filter(is.element(feature, described_features)) %>%
  arrange(desc(`All`), feature)  %>%
  mutate(Age = ifelse(Age=="children", "Child:", "Adult:")) %>%
  pivot_wider(names_from=Age, values_from=c(`All`, `Support`, `Contain`), 
              names_glue = "{Age} {.value}") %>%
  arrange(desc(`Adult: All`)) %>%
  mutate(feature = case_when(feature == 'support_response_sharpness_C=1' ~ 'Supp. Sharpness',
                             feature == 'support_probability' ~ 'Pr(support)',
                             feature == 'normed_velocity_std_after_first_collision_objects=target' ~ 'Vel(Target)',
                             feature == 'normed_velocity_std_after_first_collision_objects=drop' ~ 'Vel(Drop Obj)',
                             feature == 'avg_len' ~ 'M(Move Time)',
                             feature == 'len_std' ~ 'SD(Move Time)',
                             feature == 'obj_final_position_invstd_objects=target' ~ '1/SD(Target Pos)',
                             feature == 'obj_final_position_invstd_objects=drop' ~ '1/SD(Drop Obj Pos)',
                             feature == 'avg_final_radius_objects=target' ~ 'M(Target Dist)',
                             feature == 'avg_final_radius_objects=drop' ~ 'M(Drop Obj Dist)',
                             feature == 'avg_max_radius_objects=drop' ~ 'Max(Drop Obj Dist)',
                             feature == 'avg_max_radius_objects=target' ~ 'Max(Target Dist)',
                             TRUE ~ feature)) %>%
  rename(Feature = feature)

@@

At the same time, the fact that these results are not fully explainable by simple heuristic models suggest that this paradigm may fruitfully serve as a test bed for evaluating more complex computational theories of curiosity. 
For example, in one proposal learners prefer to explore stimuli that are "moderately discrepant" in relation to their current knowledge state, thereby providing an opportunity to learn [@Kinney1976], and curiosity changes as the gap between the learner's knowledge develops and the state of the world closes [@Loewenstein1994].
These theories are beginning to be implemented in deep neural networks, which are now capable of learning forward and inverse physical dynamics (i.e., "intuitive physics") from images when given the ability to "poke" the objects in the scene [@Agrawal2016], and have more recently been used to test which "curious" policies for generating actions result in robust and effective learning of intuitive physics in deep reinforcement learning agents [@Haber2018learning].
<!-- @Haber2018learning created a deep reinforcement learning model to drive intrinsically-motivated artificial agents, using two interacting neural networks: a *world-model* and a *self-model*.
These networks are trained simultaneously to solve different problems: the world-model attempts to predict the consequences of the agent's actions (either the forward or inverse dynamics), while the self-model attempts to learn to predict the errors of the world-model. 
The agent can use the predictions of the self-model to implement a variety of curiosity policies for choosing actions, for example to pick actions that it believes will challenge its world-model. 
-->
In future work, we aim to examine the development of curiosity in such curious artificial agents, and compare whether these agents behave similarly to people and "drop it like it's hot" [@Snoop].
The multifaceted nature of curiosity has fascinated researchers for decades, but only recently have we developed the means to factorize and test these theories. 
We propose that the development of parallel tasks for children, humans, and embodied agents is a promising way forward towards modeling curiosity in the real-world.

>>>>

## Method
### Participants
200 adults were recruited via Amazon Mechanical Turk and were paid $1 for participating.

### Materials
Stimuli were images of 3D objects produced using Blender 3D-modeling software. 
The nine objects, depicted in Figure 1, were bowl, cone, dumbbell, octahedron, pentagon (pentagonal prism), pipe, pyramid, torus, triangular prism, and ball (sphere; not pictured).

@@

### Design
The experiment consisted of 20 drop trials, completed by each participant in one of four pseudorandom orders.
Participants were randomly assigned to each order.
Each drop trial displayed an object X that is to be dropped on one of two other objects (Y or Z), as described in the following procedure.
In the 20 trials, each of the above 3D objects was used twice as the drop object (X), and appeared four times as potential targets.
Instead of randomly sampling the target objects (Y or Z), each trial was designed to allow for one of two goal relations (or affordances): containment, or support.
That is, the target objects were chosen so that one of them would be capable of either supporting or  containing the dropped object.
For example, if asked to drop the cone on either the torus or the octahedron, a containment relation could be achieved between the cone and the torus, but not the octahedron (and support is unlikely due to the small surface area of the octahedron).
An example support relation is choosing to drop the pentagonal prism on the (equal diameter) pipe rather than the pyramid.
10 of the 20 trials were designed to afford containment relations, and the other 10 afforded support relations.
We refer to the objects affording the designed containment and support relations as *targets*, and the alternative objects as *distractors*.
Distractors for each trial were the same for all participants, and were selected to 1) not afford containment/support of the dropped object, and 2) roughly equate the frequency of appearance of all 10 objects.

@@

```{r fig2-task, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=3.5, fig.height=3.4, set.cap.width=T, num.cols.cap=1, fig.cap = "Example of a trial given to adults in Experiment 1."}
img <- png::readPNG("figs/2AFC_DropTaskFig.png")
grid::grid.raster(img)
```

@@

```{r noise-ceiling, echo=F}

calc_noise_ceiling <- function(split_half_cors) {
  rD = (2 * split_half_cors) / (1 + split_half_cors)
  return(sqrt(mean(rD)))
}

noise_ceiling_adult = calc_noise_ceiling(sh_subj_adult) # .99
noise_ceiling_child = calc_noise_ceiling(sh_subj_child) # .87

#calc_noise_ceiling(sh_ch_contain) # .66
#calc_noise_ceiling(sh_ad_contain) # .96

#calc_noise_ceiling(sh_ch_support) # .88
#calc_noise_ceiling(sh_ad_support) # .97

## Results
We analyzed data from the `r Nad` adults who completed the experiment and answered at least 3 of the 4 catch trials correctly (45 participants were excluded for not meeting this criterion).
<!-- The main questions of interest are 1) are adults consistent in their preference of drop-target combinations? 2) are they more consistent with trials that afford support or containment relations? and 3) are there other apparent factors that drive their preferences? Our analysis addresses each question in turn. -->
Averaging each subject's binary responses (1=target relation, 0=alternative) for each trial type revealed a stronger preference for containment relations ($M=$ `r round(ad_rel_means[1,]$M,2)`) than support relations ($M=$ `r round(ad_rel_means[2,]$M,2)`; paired `r apa::t_apa(ad_supp_cont, format="rmarkdown", print=F)`).
Table 1 shows the proportion of participants that chose the designed target relation for each of the 20 trials. <!-- [should also show alternative target object?]. -->
Based on the binomial distribution, any of the trials on which more than 90 of the 155 participants agree (i.e., >0.59 or <0.41) significantly differ from chance. 
As can be seen in Table 1, adults participants (*adult* column) significantly preferred the target relation for all 10 of the containment trials, and significantly preferred five targets on the 10 support trials; the other five support trials did not significantly differ from chance, suggesting that many participants found the prospect of dropping on the distractor object at least equally enticing.

@@

# Experiment 2: Children

Experiment 1 demonstrated that adults show consistent preferences for dropping objects on target objects that afford containment relations, and to a lesser extent support relations. 
Experiment 2 investigates whether these strong preferences are present even in young children, recognizing that children may find different types of physical interactions (e.g., rolling, bouncing, unpredictability) of greater interest than adults, or may simply show more idiosyncratic choice patterns.

## Method
We adapted the same materials and procedure used in Experiment 1 for use in an online experiment with children, in order to directly compare the results for children and adults.

### Participants
Participants were 73 children recruited online via outreach through a local nursery school and targeted Facebook ads over the course of 6 months.
Participant exclusions were made based on cases where i) the participant did not complete more than half of the study play session or ii) the parent did not consent for video recording of study. 
After exclusions, results from `r Nch` were analyzed, including `r age[1,]$N` 3-year-olds, `r age[2,]$N` 4-year-olds, `r age[3,]$N` 5-year-olds, `r age[4,]$N` 6-year-olds, and `r age[5,]$N` 7-year-olds.

### Materials
The materials were the same as those used in Experiment 1, except that the trials were adapted for presentation via Zoom in a slide presentation as shown in Figure 3.

@@

### Procedure
<!-- Based on piloting, we estimated the activity would require 10 minutes to complete. -->
After the parent provided informed consent, children were assigned to one of two pseudorandom trial orders in counterbalanced order.
<!-- A video recording was taken of the online session. -->
To accompany the practice trial, children were shown 3D-printed instances of the three physical objects held by the researcher, to ensure that children understood their physicality. 
Children were asked to verbally select target object Y or Z, and then asked to confirm whether they wanted to select the object on the red or green side of the screen, in order to prevent left/right confusion. 
The sides on which target objects and colors appeared were counterbalanced across trials.

## Results
<!-- Were children more consistent in their choices on support or containment trials? -->
Similar to adults, averaging each child's binary responses for each trial type revealed a stronger preference for containment relations ($M=$ `r round(ch_rel_means[1,]$M,2)`) than support relations ($M=$ `r round(ch_rel_means[2,]$M,2)`; paired `r apa::t_apa(ch_supp_cont, format="rmarkdown", print=F)`). 
Unlike adults, however, children did not show a significant preference for choosing the support relation. <!-- [add a regression with trial_type * age (3 - 18=adult)?] -->
Figure 4 shows the proportion of participants' choice of the designed target relation broken down by relation type and age group. Preferences increased with age and were overall stronger for containment.

We next examined trial-level effects in children. 
Table 1 shows the proportion of children ("child" column) choosing the designed target relation for each of the 20 trials, alongside the adult choice proportions from Experiment 1. 
Based on the binomial distribution, any of the trials on which more than 41 of the 66 participants agree (i.e., >0.64 or <0.36) significantly differ (*p*<.05) from chance. 
Children significantly preferred the designed relation on eight of the 10 containment trials, while only significantly preferring two of the 10 support relation choices.
On the remaining two containment trials and the other eight support trials, children's preferences also did not significantly differ from chance against the designed relation.
These item effects were relatively reliable, though noisier than that of adults: the split-half reliability for children's choices was *r* = `r round(mean(sh_subj_child), 2)` (sd=`r round(sd(sh_subj_child), 2)`).
The split-half reliability of children's choices on containment trials was *r* = `r round(mean(sh_ch_contain), 2)` (sd=`r round(sd(sh_ch_contain), 2)`), and on support trials was *r* = `r round(mean(sh_ch_support), 2)` (sd=`r round(sd(sh_ch_support), 2)`).

@@

### Comparison of Children's vs. Adults' Preferences
<!-- Finally, we compared the trial-level preferences of children and adults. -->
Figure 5 shows adults' (Experiment 1) vs. children's (Experiment 2) choice proportions for the target relations, colored by relation type (visualizing the same data presented in Table 2, but with 95% CIs).
If adults' and children's judgments corresponded perfectly, they would fall along the dotted $y=x$ line, but children's preferences mostly fall short of that line, lying closer to the chance line ($y=0.5$).
At a glance, these results seem to support the hypothesis that "children are noisy adults" in this task as well as suggesting some consistency in the trial-level effects across development. 
This consistency also confers additional motivation for attempting to understand what drives human interest in particular physical interactions in this task through computational models.

@@

# Comparison to Physics Simulations
```{r load-model-data}
load(here("models/model_data.RData")) # mdat, all_trials_mse, all_trials_mse_r, etc.
load(here("models/support_probability_fit_df.RData")) 
# ad_df, ch_df - model (w SD) vs. human (need 95%CIs)

@@

For each trial's two possible drop object choices, we ran 250 simulated drops, and for each drop we calculated a variety of features measuring the state of the model after the drop was completed.
We selected features that we thought may provide good metrics for what people could find interesting, for instance, the mean amount of time before both objects come to rest (*M(Move Time)*), as well as the standard deviation of that time (*SD(Move Time)*).
Some features were calculated separately for drop and target objects, such as how variable each object's final positions tend to be (e.g., the inverse SD of each object's final position (*1/SD(Drop Obj Pos)* and *1/SD(Target Pos)*), the mean and maximum final distance of each object from the drop location (e.g., *M(Target Dist)* and *Max(Target Dist)*), and how variable the velocity of each object tends to be after the first collision (e.g., *SD(Target Vel)*).
<!-- SD of the normed velocity of each object after first collision (e.g.,  -->
We also tested a variety of features based on the likelihood of the dropped object coming to rest atop the target object--$Pr(support)$--and the robustness of this likelihood to small perturbations in drop position (*Supp. Sharpness*).
Note that the model's definition of support does not explicitly distinguish support from containment.

@@

Overall, a few of these features were modestly correlated with people's choices. 
Table 2 shows the correlation between model preferences (with softmax $\beta = 1$) vs. adults' and children's choice proportions, both to all trials and separately for containment and support trials.
When all trials were considered together, the feature with the strongest correlation to adults' choices was the velocity of the target object (*SD(Target Vel)*, $r=.33$), while the feature with the strongest correlation to children's choices was *Support Sharpness* (see Methods, $r=.18$)
<!-- For support trials, both adults' ($r=.39$) and children's ($r=.41$) choices were best correlated with a feature indexing the variability in the target object's final position (*1/SD(Target Pos)*).  -->
<!-- For containment trials, adults' choices were most correlated with the velocity of the dropped object (*SD(Drop Obj Vel)*, $r=.54$) which also showed a modest correlation with children's choices ($r=.41$); however, children's choices were most correlated with the maximum distance of the target object (*Max(Target Dist)*, $r=.43$).  -->
Many of the other features showed weak or even moderate negative correlations with people's choices.

Examination of the models with $\beta$ optimized, in contrast, revealed that none achieved a good fit to human preferences. 
While the best-fitting feature, *Pr(support)*, captured both adults' and children's overall mean preference for the designed target relations, it explained essentially no trial-level variation and was in fact negatively correlated with choices. 
This was not due to noisy behavioral data: while the noise ceiling on choice preferences for all trials was $r=$ `r round(noise_ceiling_adult, 2)` for adults and $r=$ `r round(noise_ceiling_child, 2)` for children, the best-fitting feature accounted for very little of that.

@@

# combine all_trials, supp_trials, and cont_trials
mod_tab <- all_trials %>% select(-mse) %>%
  rename(`All` = r) %>% 
  left_join(supp_trials) %>%
  left_join(cont_trials) %>%
  filter(is.element(feature, described_features)) %>%
  arrange(desc(`All`), feature)  %>%
  mutate(Age = ifelse(Age=="children", "Child:", "Adult:")) %>%
  pivot_wider(names_from=Age, values_from=c(`All`, `Support`, `Contain`), 
              names_glue = "{Age} {.value}") %>%
  arrange(desc(`Adult: All`)) %>%
  mutate(feature = case_when(feature == 'support_response_sharpness_C=1' ~ 'Supp. Sharpness',
                             feature == 'support_probability' ~ 'Pr(support)',
                             feature == 'normed_velocity_std_after_first_collision_objects=target' ~ 'SD(Target Vel)',
                             feature == 'normed_velocity_std_after_first_collision_objects=drop' ~ 'SD(Drop Obj Vel)',
                             feature == 'avg_len' ~ 'M(Move Time)',
                             feature == 'len_std' ~ 'SD(Move Time)',
                             feature == 'obj_final_position_invstd_objects=target' ~ '1/SD(Target Pos)',
                             feature == 'obj_final_position_invstd_objects=drop' ~ '1/SD(Drop Obj Pos)',
                             feature == 'avg_final_radius_objects=target' ~ 'M(Target Dist)',
                             feature == 'avg_final_radius_objects=drop' ~ 'M(Drop Obj Dist)',
                             feature == 'avg_max_radius_objects=drop' ~ 'Max(Drop Obj Dist)',
                             feature == 'avg_max_radius_objects=target' ~ 'Max(Target Dist)',
                             TRUE ~ feature)) %>%
  rename(Feature = feature)

@@

At the same time, the fact that these results are not fully explainable by simple heuristic models suggest that this paradigm may fruitfully serve as a test bed for evaluating more complex computational theories of curiosity. 
For example, in one proposal learners prefer to explore stimuli that are "moderately discrepant" in relation to their current knowledge state, thereby providing an opportunity to learn [@Kinney1976], and curiosity changes as the gap between the learner's knowledge develops and the state of the world closes [@Loewenstein1994].
These theories are beginning to be implemented in deep neural networks, which are now capable of learning forward and inverse physical dynamics (i.e., "intuitive physics") from images when given the ability to "poke" the objects in the scene [@Agrawal2016], and have more recently been used to test which "curious" policies for generating actions result in robust and effective learning of intuitive physics in deep reinforcement learning agents [@Haber2018learning].
<!-- @Haber2018learning created a deep reinforcement learning model to drive intrinsically-motivated artificial agents, using two interacting neural networks: a *world-model* and a *self-model*.
These networks are trained simultaneously to solve different problems: the world-model attempts to predict the consequences of the agent's actions (either the forward or inverse dynamics), while the self-model attempts to learn to predict the errors of the world-model. 
The agent can use the predictions of the self-model to implement a variety of curiosity policies for choosing actions, for example to pick actions that it believes will challenge its world-model. 
-->
In future work, we aim to examine the development of curiosity in such curious artificial agents, and compare whether these agents behave similarly to people and "drop it like it's hot" [@Snoop].

The multifaceted nature of curiosity has fascinated researchers for decades, but only recently have we developed the means to factorize and test these theories. 
We propose that the development of parallel tasks for children, humans, and embodied agents is a promising way forward towards modeling curiosity in the real-world.
